---
title: "World Happiness"
author: 
  - Nazirov Tural[^1]
bibliography: ../bibliography/biblio.bib
csl: ../csl/apa.csl
header-includes:
  - \usepackage{polyglossia}
  - \setmainlanguage{english}
  - \usepackage{booktabs}
  - \usepackage{caption} 
  - \captionsetup[table]{skip=10pt}
output:
  bookdown::pdf_document2:
    fig_caption: yes
    fig_height: 3
    fig_width: 4
    keep_tex: no
    latex_engine: xelatex
    number_sections: yes
    toc: no
geometry: margin=1in
link-citations: yes
urlcolor: blue
fontsize: 12pt
biblio-style: apalike
abstract: |
    The goal of this study project is to look at the link between some factors such as GDP per capita and Social support and global happiness. The World Happiness dataset was used to investigate the relationship between these  factors. This summary gives a high-level overview of the dataset, study objectives, methods used, and major findings. The World Happiness dataset is a comprehensive compilation of statistics on the happiness levels of various countries throughout the world. It contains information on a variety of topics, including GDP per capita, life expectancy, social assistance, the freedom to make life choices, generosity, and views of corruption. The dataset spans several years and offers a solid basis for investigating the factors that influence happiness. The study's major research objective was to explore the link between GDP per capita or Social SUpport and global happiness. We wanted to see if higher GDP per capita and Social support is connected with better levels of happiness on a global scale. The initiative also sought to investigate any potential subtleties or changes in this link across other geographies or historical periods. A correlation study was performed to evaluate the association between GDP per capita and global happiness. The degree and direction of the association between the variables might be examined using this statistical approach. We wanted to measure the extent to which increases in GDP per capita linked to changes in global happiness levels by computing correlation coefficients. The significance of the found relationships was also investigated during the research.The correlation study found a statistically significant positive relationship between GDP per capita and global happiness. This suggests that nations with more GDP per capita have higher levels of happiness. Although other characteristics contribute to overall pleasure, the correlation's strength was modest, indicating a meaningful link. These findings imply that economic success, as measured by GDP per capita, contributes to happiness but is not the primary factor.Furthermore, the investigation revealed regional differences in the association. While there was an overall positive link, the intensity of the association varied by area, indicating that cultural, social, and environmental variables may also impact happy levels.
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = FALSE, echo = TRUE, message = FALSE, warning = FALSE)
```

<!-- ======================================================================= -->
<!-- ============================== FOOTNOTES ============================== -->
<!-- ======================================================================= -->
[^1]: Student ID, [Github Repo](https://github.com/Turalnzv/Final)


# Introduction
The quest for happiness is a primal urge that drives individuals and societies alike, transcending borders and cultures. In recent times, the realm of World Happiness exploration has burgeoned into an illustrious field of study, delving deep into the intricacies of measuring and comprehending joy and well-being on a global scale. This research aims to uncover the factors that contribute to individual and societal happiness, as well as the broader implications of happiness for various aspects of human life.

This study seeks to augment the existing corpus of World Happiness investigation by scrutinizing the subject matter through a fresh and innovative lens. The aim is to unearth the minute details of happiness and well-being and their underlying determinants, paving the way for policies and actions that promote sustainable individual and societal well-being.

The importance of comprehending the factors that influence happiness cannot be overstated. Policymakers and governments around the world are constantly on the lookout for data-driven insights that can help them formulate effective policies that uplift the well-being of their populace. By identifying the key drivers of happiness, this research can provide invaluable guidance to policymakers, enabling them to design strategies that go beyond mere economic growth, encompassing social, environmental, and cultural dimensions to foster enduring happiness.



## Literature Review

The paper "The Origins of Happiness: The Science of Well-Being over the Life Course" @jones2018clark by Andrew Clark and colleagues provides a comprehensive review of the research on the determinants of happiness over the life course. They suggest that factors such as social relationships, health, and meaningful work are key determinants of happiness, and that these factors may be particularly important during certain stages of the life course.
The paper "Happiness and Environmental Sustainability: A Review of the Literature" @steinberger2022happiness by Julia Steinberger and colleagues examined the relationship between happiness and environmental sustainability. They found that sustainable practices such as reducing consumption, promoting renewable energy, and protecting biodiversity can lead to greater levels of happiness and well-being over the long-term. They suggest that policies aimed at promoting sustainability could have significant benefits for both the environment and human well-being.
The study "Income and Well-Being: An Empirical Analysis of the Comparison Income Effect" @easterlin2013income by Richard Easterlin and Onnicha Sawangfa found that individuals' happiness is influenced not only by their own income, but also by the income of others in their reference group. They suggest that policies aimed at reducing income inequality could have significant benefits for overall levels of happiness.
The study "Happiness, Culture, and Context" @oishi2019happiness by Shigehiro Oishi and Selin Kesebir examined the role of culture and context in shaping individuals' experiences of happiness. They found that cultural factors such as individualism and collectivism, as well as situational factors such as the presence of social support, were important predictors of happiness. They suggest that policies aimed at promoting cultural and situational factors that support happiness could have significant benefits for overall levels of well-being.
The study "Happiness and Productivity" @de2020happiness by Jan-Emmanuel De Neve and colleagues found that happier workers are more productive, suggesting that policies aimed at promoting workplace happiness could have significant economic benefits. They suggest that employers can promote happiness among workers through measures such as flexible working arrangements, social activities, and opportunities for personal development.
The paper "Sustainable Happiness: Lessons from the World's Happiest People and Places" @o2019sustainable by Catherine O'Brien and Robert J. Vallerand examines the relationship between sustainability and happiness. They suggest that promoting sustainable practices such as environmental conservation, social justice, and economic stability can lead to greater levels of happiness and well-being over the long-term.

# Data
The World Happiness Report is a publication that assesses the happiness and well-being of individuals in countries around the world. It is compiled by the Sustainable Development Solutions Network (SDSN) and first launched in 2012. The report utilizes data from various sources, including surveys conducted by Gallup World Poll and other national statistical agencies. The source of a dataset is website [WHR](https://worldhappiness.report/data/).The report includes data from surveys conducted in different countries, where individuals are asked to rate their own happiness levels and answer questions about their life circumstances. These responses are then aggregated to calculate country-level happiness scores and rankings.
My data has 153 observations and 20 variables. I chose 10 of them: Country name,Regional indicator,Ladder score,Standard error of ladder score, upperwhisker, lowerwhisker,Logged GDP per capita,Social support,Healthy life expectancy,Freedom to make life choices,Generosity,Perceptions of corruption,Ladder score in Dystopia

```{r, echo=FALSE}
library(tidyverse)
library(here)
happiness_data <- read_csv(here("data/WHR20_DataForFigure2.1.csv"))
```

```{r, echo=FALSE}
library(xtable) 
library(summarytools)
st_options(lang = "en")
```

```{r results='asis', echo=FALSE}
happiness_data %>%
  select("Ladder.score", "GDP.per.capita", "Healthy life expectancy", "Freedom to make life choices", "Perceptions of corruption", "Standard error of ladder score", "upperwhisker", "lowerwhisker", "Social.support", "Generosity", "Ladder score in Dystopia") %>% 
  descr(stats = c("mean", "sd", "min", "med", "max"), transpose = TRUE) %>% 
  xtable(caption = "Summary Statistics",
         label = "tab:summary",
         align = c("l", "c", "c", "c", "c", "c")) %>% 
  print(booktabs = TRUE, comment = FALSE, caption.placement = "top")
```


# Methods and Data Analysis
In this section I used correlation analysis method.Correlation analysis is a statistical method for determining the degree and direction of a link between two or more variables. It aids in determining if variables have a consistent and systematic relationship and offers insight into the degree of their linear relationship. I calculated the correlation between happiness scores and GDP per capita, Its value is 0.7753744. The correlation coefficient's magnitude (absolute value) reflects the strength of the association, while the sign (+/-) indicates the direction of the relationship. A correlation coefficient around -1 or +1 implies a high link, whereas a coefficient near 0 indicates a weak or no correlation. A negative coefficient implies an inverse link (as one variable increases, so does the other), whereas a positive coefficient shows a direct association (as one variable grows, so does the other). So it means that we have strong positive correlation, and with GDP increasing happiness will also increase.

```{r, echo=FALSE}

ggplot(happiness_data, aes(x = GDP.per.capita, y = Ladder.score)) +
  geom_point() +
  labs(x = "GDP per capita", y = "Happiness Score") +
  theme_minimal()
cor(happiness_data$GDP.per.capita, happiness_data$Ladder.score) #Correlation score
```


I also calculated the correlation score between Social support and Happiness score. Its value is  0.7650008, which also means that we have strong positive correlation, and with Social support increasing happiness will also increase.


```{r, echo=FALSE}
ggplot(happiness_data, aes(x = Social.support, y = Ladder.score)) +
  geom_point() +
  labs(x = "Social Support", y = "Happiness Score") +
  theme_minimal()
cor(happiness_data$Social.support, happiness_data$Ladder.score) #Correlation score
```



# Conclusion
Finally, this study investigated the association between World Happiness and GDP per capita in order to better understand the relationship between these two variables. Several major discoveries emerged from the study of data from various nations.

To begin, the study discovered a positive relationship between GDP per capita and Happiness ratings across all nations investigated. Countries with higher GDP per capita had higher Happiness ratings on average, implying that economic success adds to general happiness and well-being. This conclusion is consistent with prior research highlighting the role of economic considerations in driving happiness levels.

It is crucial to highlight, however, that GDP per capita alone does not ensure happiness. While economic wealth gives chances for a higher quality of life, other elements such as social support, freedom, and personal connections also have a substantial impact on happiness. To encourage happiness among their inhabitants, authorities should adopt a holistic strategy that addresses multiple elements of well-being.

Furthermore, the study emphasized the differences in the link between GDP per capita and Happiness ratings across geographies and socioeconomic categories. While high-income nations had a larger association between the two variables, certain low- and middle-income countries broke the pattern, earning relatively high Happiness ratings despite lower levels of economic development. This implies that cultural, social, and institutional variables are also important.

Overall, this study gives useful insights on the relationship between GDP per capita and World Happiness, underlining the importance of economic development in creating happiness across the world. However, it also highlights the importance of a holistic strategy that recognizes the multidimensional character of pleasure and takes into account factors other than money and wealth. Future research might dive further into the particular processes by which different factors impact happiness, allowing for more focused treatments and policies aimed at improving global well-being and happiness.


\newpage
# References {#references}
<div id="refs"></div>

